---
title: "ToothGrowth"
output: word_document
---

### Overview

For this excercise, we will look at the data for the ToothGrowth dataset, and determine which variables have an impact on the growth of teeth. 

### Review of the Data 

First, we need to look at the data to understand the variables and the overall summary. 
```{r}
head(ToothGrowth)
summary(ToothGrowth)
```

Next, it will be helpful to see some graphs of the main variables: length, supplement, and dose. 

```{r, echo=FALSE}
library(ggplot2)
ggplot(data=ToothGrowth, aes(x=as.factor(dose), y=len)) + 
  geom_bar(stat="identity",position=position_dodge()) +
    facet_grid(. ~ supp) +
    xlab("Dose") +
    ylab("Length")
```


### T Test for Supp

Having reviewed our data, we should now begin looking at how t-tests compare across the variables. 

```{r}
t.test(len ~ supp, ToothGrowth, var.equal = FALSE)
```

Unfortunately, given that the p-value is above 0.05, the data is not statistically significant and we cannot reject the null hypothesis. 

### T Test for Dose 

Next, we will need to complete t-tests for the various dose levels. 

```{r}
t.test(ToothGrowth$len[ToothGrowth$dose == 2],ToothGrowth$len[ToothGrowth$dose == 1])
```

```{r}
t.test(ToothGrowth$len[ToothGrowth$dose == 2],ToothGrowth$len[ToothGrowth$dose == 0.5])
```

```{r}
t.test(ToothGrowth$len[ToothGrowth$dose == 1],ToothGrowth$len[ToothGrowth$dose == 0.5])
```

Given that all three levels have a p-value of less than 0.05, we can reject the null hypothesis for all three cases. 

### Conclusion 

Based on our conclusion, different dosages can have an effect on the length of teeth. However, the supplement does not. 
