---
title: "SI Final Project PArt 1"
output: word_document
---

##Overview

For part I of the project, I will comaring the exponential distribution in R and with the Central Limit Theorem.  I will be utilizing the formula rexp(n, lambda) where lambda is the rate parameter.  The mean of exponential distribution is 1/lambda and the standard deviation is also 1/lambda.Specifically, I will be using 0.2 for lamda, with a distribution of averages of 40 exponentials. 

##Simulations

First, I put together the simulation using the formula provided. I set the seed so that this could be reproduced. 

```{r}
set.seed(5)
lambda <- 0.2
samp_size <- 40
n <- 1000

sim <- matrix(rexp(n*samp_size, rate=lambda), n, samp_size)
means <- rowMeans(sim)
```

Sample Mean and Variance versus Theoretical Mean and Variance:

Next, I will plot the historgram with both the distribution of the simulation versus that of the theoretical. 

```{r, echo=FALSE}
hist(means, breaks=100, prob=TRUE,
     main="Simulation vs. Theoretical Distribution",
     xlab="")

# density of the averages of samples
lines(density(means), col="blue")

# center of the sample averages
abline(v=mean(means), col="blue")

# theoretical center of distribution
abline(v=1/lambda, lty=2, col="red")

# theoretical density of the averages of samples
xfit <- seq(min(means), max(means), length=100)
yfit <- dnorm(xfit, mean=1/lambda, sd=(1/lambda/sqrt(samp_size)))
lines(xfit, yfit, pch=22, col="red", lty=2)

# add legend
legend('topright', c("simulation", "theoretical"), lty=c(1,2), col=c("blue", "red"))
```

The sample mean can be seen by the vertical blue line, just to the right of the theoretical red dotted line. 

##Distribution 

Above, you can see that the theoretical mean and the sample mean are very close. This is because, given by the central limit theorem, the larger the sample size, the liklier the sample will show a normal distribution.  

